Check Coverage

### 2020-09-08 analysis/merge_data.Rmd
Add number of plots to each study.

Create table of info for each study
```{r}
study_table <- biotime_data %>%
  group_by(study_id) %>%
  mutate(min_year = min(year), max_year = max(year), n_year = n_distinct(year)) %>% 
  #select(study_id, plot, taxa, latitude, longitude, min_year, max_year) %>%
  select(study_id, taxa, min_year, max_year) %>%
  distinct() %>%
  left_join(coverage %>% select(study_id, coverage = perc), by = "study_id")

>>>>

Create table of info for each study
```{r}
study_table <- biotime_data %>%
  group_by(study_id) %>%
  mutate(min_year = min(year), max_year = max(year), n_year = n_distinct(year), plots = n_distinct(plot)) %>% 
  select(study_id, taxa, min_year, max_year, plots) %>%
  distinct() %>%
  left_join(coverage %>% select(study_id, coverage = perc), by = "study_id")
